Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r Running at}
if (!exists('now')) {
    now <- format(Sys.time(), '%Y%m%d-%H%M%S')
}
now
```

@@

```{r Officer importer, code = sessionInfo()}
```

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
```

@@

maaslin

@@

colnames(maas.lacto.results.df.signf)
maas.lacto.results.df.signf %>%
    select(Variable, Feature, P.value, Q.value) %>%
    arrange(Q.value) %>%
    kable
```

>>>>

```{r Running at}
now <- ifelse(exists('now'),now, format(Sys.time(), '%Y%m%d-%H%M%S'))
```

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
library(pander)
```

@@

```{r Session info}
pander(sessionInfo(), compact = TRUE)
```

@@

@@

maas.lacto.results.df.signf %>%
    select(Variable, Feature, P.value, Q.value) %>%
    arrange(Q.value) %>%
    kable
```
